Tail associations and their impact on extinction risk

### 2019-10-27 MainText.Rmd
need to revisit why we used 6 of cohen's models and not the other two

<!--density-dependence metapopulation model-->
To investigate Q2 from the \nameref{Introduction}, we considered spatialized, stochastic versions
of six density dependent population models, the Ricker, Hassell, Maynard Smith, Pennycuick, Verhulst, 
and Austin-Brewer models (@cohen1995unexpected; Table \ref{tab_model_summary}).
All models took the general form $\vec{P} (t+1) = D \lambda(t) \vec{P}(t)$,
where $\vec{P}(t)$ is a vector of population densities, 
the $i^{\text{th}}$ component $P_i(t)$ representing
the population density in the $i^{\text{th}}$ habitat patch ($i=1,2,\ldots,n$) at time $t$. 
The $n \times n$ matrix $\lambda(t)$ was diagonal with $i^{\text{th}}$ diagonal entry 
$\lambda_i(t)$ depnding on the model used (see Table \ref{tab_model_summary}). The matrix $D$
was an $n \times n$ dispersal matrix. For simplicity, 
we assumed the $n$ habitat patches were arranged, evenly spaced, in a line.
We considered both "local" and "global" dispersal among patches in different simulations. 
For local dispersal, a fraction $d$ of 
each population dispersed during each time step, equally distributed to
the two or one nearest neighbors. For global dispersal the same fraction $d$ dispersed
equally to the other $(n-1)$ patches. When $d$ was $0$, dispersal did not occur and 
rescue effects were not possible.
Two models that @cohen1995unexpected used were excluded from our analyses because they were not
readily adapted to our simulation setup: the Varley model,
which is not continuous;
<!--***DAN: Shyamolina, looking back at the Cohen paper, using the value C=1 as they used, the
Varley model *is* continuous. It is not differentiable, but it's not clear to me that 
non-differentiability means we cannot use the model. Let's discuss.-->
and the Malthus-Condorcet-Mill model, which employs a logarithm of the population and therefore
cannot be applied in the context of extinction.
<!--***DAN: go back and look at that model when you get the paper and remind yourself-->

>>>>

<!--density-dependence metapopulation model-->
To investigate Q2 from the \nameref{Introduction}, we considered spatialized, stochastic versions
of six density dependent population models, the Ricker, Hassell, Maynard Smith, Pennycuick, Verhulst, 
and Austin-Brewer models (@cohen1995unexpected; Table \ref{tab_model_summary}).
All models took the general form $\vec{P} (t+1) = D \lambda(t) \vec{P}(t)$,
where $\vec{P}(t)$ is a vector of population densities, 
the $i^{\text{th}}$ component $P_i(t)$ representing
the population density in the $i^{\text{th}}$ habitat patch ($i=1,2,\ldots,n$) at time $t$. 
The $n \times n$ matrix $\lambda(t)$ was diagonal with $i^{\text{th}}$ diagonal entry 
$\lambda_i(t)$ depnding on the model used (see Table \ref{tab_model_summary}). The matrix $D$
was an $n \times n$ dispersal matrix. For simplicity, 
we assumed the $n$ habitat patches were arranged, evenly spaced, in a line.
We considered both "local" and "global" dispersal among patches in different simulations. 
For local dispersal, a fraction $d$ of 
each population dispersed during each time step, equally distributed to
the two or one nearest neighbors. For global dispersal the same fraction $d$ dispersed
equally to the other $(n-1)$ patches. When $d$ was $0$, dispersal did not occur and 
rescue effects were not possible.
Two models that @cohen1995unexpected used were excluded from our analyses because they were not
readily adapted to our simulation setup: the Varley model,
which is not continuous;
<!--***DAN: Shyamolina, looking back at the Cohen paper, using the value C=1 as they used, the
Varley model *is* continuous. It is not differentiable, but it's not clear to me that 
non-differentiability means we cannot use the model. Perhaps it does mean that, but I don't see 
it. Let's discuss. I'm not saying we have to go back and use it, but we may have to justify
differently why we used 6 of Cohen's models and not the other two.-->
and the Malthus-Condorcet-Mill model, which employs a logarithm of the population and is therefore
inconvenient to analyze in the context of extinction.
<!--***DAN: Unless I am mistaken, the limit of the right hand side of the M-C-M model as
described by Cohen, as P approaches 0 from the right, is 0. That means the model has
a removable singularity at 0, i.e., we could just define the model so P_t+1=0 when P_t
is 0, and we would get a perfectly valid continuous model. This means that using logs is 
not really a valid reason to not use the models. Let's discuss. I'm not saying we have to go 
back and use it, but we may have to justify differently why we used 6 of Cohen's models and not 
the other two.-->
